The \dealii Library, Version 9.5

### 2023-07-06 9.5/paper.tex
write first CMake paragraph

>>>>

\dealii's original CMake build system that was merged for the 8.0.0 release
in 2013 was written for CMake 2.8.8, which, naturally, lacks many of the
modern features introduced into CMake over the last couple of years. This
created a particular issue with an increasing number of dependencies
switching their CMake configuration to \emph{import targets}, where all
necessary information for using an external resource, such as include
directories and library link interfaces, are associated with an imported
CMake targets rather than being provided with individual (and
inconsistently) named CMake variables. With the \dealii 9.5 release the
handling of external dependencies has been rewritten entirely to support
imported targets. The \trilinos and \kokkos interfaces have been
modernized. We plan to migrate all remaining dependencies to import targets
wherever possible for the next release.
